Abstract Data Type Inference

### 2015-03-22 nature.tex
Added lots of patterns.

THIS IS THE SET OF PATTERNS
\begin{align*}
  & \mathrm{read}:\_ \\
  & \underline{\mathrm{write}:1}\ \underline{\mathrm{read}:2} \\
  & \mathrm{read}:1\ \underline{\mathrm{write}:1} \\
  & \underline{\mathrm{write}:1}\ \underline{\mathrm{write}:2}\ \mathrm{read}:1
\end{align*}
The atomic register ADT is predictable \ldots

@@

@@

@@

\subsection{The Priority Queue (?)}

@@

\subsection{The Atomic Semaphore}

\subsection{The Rendezvous Synchronizer}

\subsection{The Exchanger}

\subsection{The Barrier}

ANY OTHERS??

>>>>

THIS IS THE SET OF PATTERNS

\begin{verbatim}
  [1:X] read => 1 (RO)  #
  --
  [1:1] write(1)            #
  [2:2] read => empty (RO)    #
  --
  [1:2] read => 1 (RO)  #
  [2:2] write(1)          #
  --
  [1:1] write(1)        #
  [2:2] write(2)          #
  [3:1] read => 1 (RO)      #
\end{verbatim}

The atomic register ADT is predictable \ldots

@@

\begin{verbatim}
  [1:_] remove => 1  #
  --
  [1:1] add(1)                #
  [2:2] remove => empty (RO)    #
  --
  [1:2] remove => 1  #
  [2:2] add(1)         #
  --
  [1:1] add(1)       #
  [2:2] add(2)         #
  [3:2] remove => 2      #
  --
  [1:1] add(1)       #
  [2:1] remove => 1    #
  [3:1] remove => 1      #
  --
  [1:1] add(1)                #
  [2:2] remove => empty (RO)    #
  [3:1] remove => 1               #
  --
  [1:1] add(1)       #
  [2:2] add(2)         #
  [3:2] remove => 2      #
  [4:1] remove => 1        #
\end{verbatim}

@@

\begin{verbatim}
  [1:_] remove => 1  #
  --
  [1:1] add(1)                #
  [2:2] remove => empty (RO)    #
  --
  [1:2] remove => 1  #
  [2:2] add(1)         #
  --
  [1:1] add(1)       #
  [2:2] add(2)         #
  [3:1] remove => 1      #
  --
  [1:1] add(1)       #
  [2:1] remove => 1    #
  [3:1] remove => 1      #
  --
  [1:1] add(1)                #
  [2:2] remove => empty (RO)    #
  [3:1] remove => 1               #
  --
  [1:1] add(1)       #
  [2:2] add(2)         #
  [3:1] remove => 1      #
  [4:2] remove => 2        #
\end{verbatim}

@@

\begin{verbatim}
  [1:_] insert(1) => 1 (RO)  #
  --
  [1:_] remove(1) => 1  #
  --
  [1:_] contains(1) => 1 (RO)  #
  --
  [1:1] insert(1) => empty       #
  [2:2] remove(1) => empty (RO)    #
  --
  [1:1] insert(1) => empty         #
  [2:2] contains(1) => empty (RO)    #
  --
  [1:1] insert(1) => empty  #
  [2:1] remove(1) => 1        #
  [3:1] remove(1) => 1          #
  --
  [1:1] insert(1) => empty     #
  [2:1] remove(1) => 1           #
  [3:1] contains(1) => 1 (RO)      #
  --
  [1:1] insert(1) => empty       #
  [2:2] remove(1) => empty (RO)    #
  [3:1] remove(1) => 1               #
  --
  [1:1] insert(1) => empty         #
  [2:2] contains(1) => empty (RO)    #
  [3:1] remove(1) => 1                 #
\end{verbatim}

@@

\begin{verbatim}
  [1:_] lock(1) => 1 (RO)  #
  --
  [1:_] unlock => 1  #
  --
  [1:1] lock(1) => empty  #
  [2:2] lock(2) => empty    #
  --
  [1:1] lock(1) => empty      #
  [2:2] unlock => empty (RO)    #
  --
  [1:1] lock(1) => empty  #
  [2:2] lock(2) => empty    #
  [3:1] unlock => 1           #
  --
  [1:1] lock(1) => empty  #
  [2:2] lock(2) => empty    #
  [3:2] unlock => 2           #
  --
  [1:1] lock(1) => empty   #
  [2:1] unlock => 1          #
  [3:1] lock(2) => 1 (RO)      #
  --
  [1:1] lock(1) => empty  #
  [2:1] unlock => 1         #
  [3:1] unlock => 1           #
  --
  [1:1] lock(1) => empty      #
  [2:2] unlock => empty (RO)    #
  [3:1] unlock => 1               #
  --
  [1:1] lock(1) => empty  #
  [2:2] lock(2) => empty    #
  [3:1] unlock => 1           #
  [4:2] unlock => 2             #
  --
  [1:1] lock(1) => empty  #
  [2:2] lock(2) => empty    #
  [3:2] unlock => 2           #
  [4:1] unlock => 1             #
\end{verbatim}

\subsection{Work-Stealing Queue}

TODO THERE ARE 24 PATTERNS FOR EACH OF THE 4 VARIATIONS

NOTE LIMITATIONS: PRIORITY QUEUE, SEMAPHORE, RENDEZVOUS SYNCHRONIZER,
EXCHANGER, BARRIER, …
